---
title: "Coral Heat Stress"
author: "Grace Beery, Hayden Dickerson, Susritha Kopparapu"
date: "3/27/2021"
output: html_document
---
*The following script is modified from Sarah Davies and James Fifer*

## Introduction

## Setup

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#### R Version
R version 4.0.2 was used for this analysis. 

#### Packages
The following packages were used to clean, analyze, and visualize data. Packages were installed with [Bioconductor](https://bioconductor.org/biocLite.R) version 3.12.  
```{r, message=FALSE}
library("affycoretools")            #Version 1.60.1
library("arrayQualityMetrics")      #Version 3.44.0
library("genefilter")               #Version 1.70.0
library("DESeq2")                   #Version 1.28.1
library("ggplot2")                  #Version 3.3.3
library("dplyr")                    #Version 1.0.1
library("pheatmap")                 #Version 1.0.12
library("vegan")                    #Version 2.5.7
library("ggrepel")                  #Version 0.8.2
library("tidyverse")                #Version 1.3.0
```

```{r, eval=FALSE, echo=FALSE}
packageVersion("affycoretools")
packageVersion("arrayQualityMetrics")
packageVersion("genefilter")
packageVersion("DESeq2")
packageVersion("ggplot2")
packageVersion("dplyr")
packageVersion("pheatmap")
packageVersion("vegan")
packageVersion("ggrepel")
packageVersion("tidyverse")
```

## Outlier Analysis 

## Raw Counts Analysis

## Deseq

-----------------------

## Pairwise comparison between hot and control 

## GO table for MWU

## P values and Rlogdata

-----------------------
## Heat map of sample distances

## PCA

## Heat map for genes 

## Heat map for genes in common 
-----------------------

## Conclusion 



